---
title: "Nimalarragan Invertebrate Analysis"
author: "Adrian Pinder"
date and time: '`r Sys.time()`'
output: html_document
software: 'RStudio: Version 1.1.463 – © 2009-2018 RStudio, Inc. R version: `r getRversion()`'
editor_options: 
  chunk_output_type: console
---
  
Git repository https://github.com/AdrianMP62/Nimalarragan  

RStudio: Version 1.1.463 – © 2009-2018 RStudio, Inc. R version: `r getRversion()`  
Date and time: `r Sys.time()`

Uses the following datafiles:  
*  Invert_matrix.csv (System,	SurveyType,	SiteName,	SiteCode,	Subsite	Date,	CommonName,	SpeciesCode,	Count) (e.g. Warden,	aerial,	Neridup Suite,	WRP001,	combined,	11/10/2006,	Great Egret,	greg,	1)



Date and time: `r Sys.time()`

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(include = FALSE)
```

```{r}
options(scipen=999)
```

```{r results="hide", warning=FALSE, message=FALSE}
Packages <- c("vegan","cluster","data.table", "ggrepel", "ggplot2", "stringr", "reshape2", "knitr", "simba", "zoo", "car")
lapply(Packages, library, character.only = TRUE)
#source("./functions/bio_env_ext.R") #The Bio_env and bv_step_ext routines below comes from http://menugget.blogspot.com.au/2011/06/clarke-and-ainsworths-bioenv-and-bvstep.html
```

```{r}
set.seed(1234)
```

#Ionic composition analysis
```{r}
#load data files
MgL.data <- read.csv("FVS ionic compositions.csv", row.names=1)
MgL.data <- MgL.data[, 1:8]

Meq.data <- MgL.data
Meq.data$Na <- Meq.data$Na*0.0435
Meq.data$Ca <- Meq.data$Ca*0.0499
Meq.data$Mg <- Meq.data$Mg*0.0823
Meq.data$K <- Meq.data$K*0.0256
Meq.data$Cl <- Meq.data$Cl*0.0282
Meq.data$SO4 <- Meq.data$SO4*0.0208
Meq.data$HCO3 <- Meq.data$HCO3*0.0164
Meq.data$CO3 <- Meq.data$CO3*0.0333


Totals.cations <- rowSums(Meq.data[,1:4])
Totals.cations
Totals.anions <- rowSums(Meq.data[,5:8])
Totals.anions

Balance <- (Totals.anions - Totals.cations)/Totals.anions
Balance

Meq.data$Napercent <- Meq.data$Na/Totals.cations*100
Meq.data$Capercent <- Meq.data$Ca/Totals.cations*100
Meq.data$Mgpercent <- Meq.data$Mg/Totals.cations*100
Meq.data$Kpercent <- Meq.data$K/Totals.cations*100
Meq.data$Clpercent <- Meq.data$Cl/Totals.anions*100
Meq.data$SO4percent <- Meq.data$SO4/Totals.anions*100
Meq.data$HCO3percent <- Meq.data$HCO3/Totals.anions*100
Meq.data$CO3percent <- Meq.data$CO3/Totals.anions*100

write.csv(Meq.data, "Meqdata3.csv")
```


#Analyses of invertebrate samples from Nimalarragan wetland north of Broome
  
##Import data
```{r import-and-restructure-Warden-and-Gore-waterbird-data}
input.data <- read.csv("./raw_data/Invert_matrix.csv")
input.data$sample_long <- paste(input.data$SiteCode, input.data$Sample, sep = " ")
input.data$taxon <- paste(input.data$LowestIDNC, input.data$LowestID, sep = " ") 
input.data$taxon <- gsub(" ", "_", input.data$taxon)
```

##Create matrix
```{r create-matrix-for-ordination}
invert.matrix <- melt(input.data) #melt data 
  invert.matrix <- dcast(invert.matrix, sample_long ~ taxon, fill="0") #create matrix from flat-file
  rownames(invert.matrix) <- invert.matrix [,1] #use first column (season) as row.names
  invert.matrix [,1] <- NULL #remove season column
  invert.matrix <- data.matrix(invert.matrix, rownames.force = NA) #convert data to numeric format
  #invert.matrix <- t(invert.matrix)
write.csv(invert.matrix, "./outputs/invert_matrix.csv")
```

##create plankton and benthic only matrices
```{r}
invert.matrix.P <- invert.matrix[grep("P", row.names(invert.matrix)), ]
  invert.matrix.P <- invert.matrix.P[, colSums(invert.matrix.P)>0 ]
  write.csv(invert.matrix.P, "./outputs/invert_matrix_P.csv")
invert.matrix.B <- invert.matrix[grep("B", row.names(invert.matrix)), ]
  invert.matrix.B <- invert.matrix.B[, colSums(invert.matrix.B)>0 ]
  write.csv(t(invert.matrix.B), "./outputs/invert_matrix_B.csv")
```

#remove or merge rows to create taxonomically consistent datasets
```{r}
#PLANKTON
#specify rows to remove - creating new data file
invert.matrix.Pred <- subset(invert.matrix.P, select=-c(IF999999_Turbellaria,JB999999_Bdelloidea,MM239999_Arrenuridae,MM999901_Acarina,QC0999A6_Bidessini,QC110499_Berosus_sp.,QD099999_Ceratopogonidae,QH520199_Mesovelia_sp.,QH670499_Anisops_sp.,QO021099_Ischnura_sp.,QO129999_Aeshnidae))
invert.matrix.Pred <- as.data.frame(invert.matrix.Pred) #convert to data.frame to allow calculations
#merge Gerridae with Limnogonus and delete Gerridae
invert.matrix.Pred$QH570399_Limnogonus_sp. <- pmax(invert.matrix.Pred$QH570399_Limnogonus_sp., invert.matrix.Pred$QH579999_Gerridae)
invert.matrix.Pred$QH579999_Gerridae <- NULL #delete Gerridae
#merge Pleidae with P.brunni and delete P. brunni
invert.matrix.Pred$QH680199_Paraplea_sp. <- pmax(invert.matrix.Pred$QH680199_Paraplea_sp., invert.matrix.Pred$QH680101_Paraplea_brunni)
invert.matrix.Pred$QH680101_Paraplea_brunni <- NULL #delete Gerridae

#BENTHIC
#specify rows to remove - creating new data file
invert.matrix.Bred <- subset(invert.matrix.B,select=-c(II999999_Nematoda,MM9999A1_Oribatida_sp.,MM9999A2_Mesostigmata,MM9999A6_Trombidioidea,QC0999A6_Bidessini,QC110499_Berosus_sp.,QC119999_Hydrophilidae,QD070799_Culex_sp.,QD099999_Ceratopogonidae,QH610299_Ranatra_sp.,QH670499_Anisops_sp.,QH670499_Anisops_sp.,QO179999_Libellulidae))
invert.matrix.Bred <- as.data.frame(invert.matrix.Bred) #convert to data.frame to allow calculations
#merge Limbodessus sp. and L. compactus
invert.matrix.Bred$QC091099_Limbodessus_sp. <- pmax(invert.matrix.Bred$QC091099_Limbodessus_sp., invert.matrix.Bred$QC091001_Limbodessus_compactus)
invert.matrix.Bred$QC091099_Limbodessus_sp. <- NULL #delete Limbodessus compactus
#merge Cybister sp. and C. tripunctatus
invert.matrix.Bred$QC093699_Cybister_sp. <- pmax(invert.matrix.Bred$QC093699_Cybister_sp., invert.matrix.Bred$QC093606_Cybister_tripunctatus_temnenkii)
invert.matrix.Bred$QC093606_Cybister_tripunctatus_temnenkii <- NULL #delete Cybister tripunctatus
#merge Tramea with tramea stenoloba/loewii
invert.matrix.Bred$QO172899_Tramea_sp. <- pmax(invert.matrix.Bred$QO172899_Tramea_sp., invert.matrix.Bred$QO1728A0_Tramea_stenoloba_loewii)
invert.matrix.Bred$QO1728A0_Tramea_stenoloba_loewii <- NULL #delete Tramea stenoloba-loewii
#merge naucoris with N. opacus
invert.matrix.Bred$QH660199_Naucoris_sp. <- pmax(invert.matrix.Bred$QH660199_Naucoris_sp., invert.matrix.Bred$QH660103_Naucoris_subopacus)
invert.matrix.Bred$QH660103_Naucoris_subopacus <- NULL #delete Naucoris_subopacus
#merge Gerridae with Limnogonus and L. fossarum giluy
invert.matrix.Bred$QH570399_Limnogonus_sp. <- pmax(invert.matrix.Bred$QH570399_Limnogonus_sp., invert.matrix.Bred$QH579999_Gerridae,invert.matrix.Bred$QH570301_Limnogonus_fossarum_gilguy)
invert.matrix.Bred$QH579999_Gerridae <- NULL #delete Gerridae
invert.matrix.Bred$QH570301_Limnogonus_fossarum_gilguy <- NULL #remove Limnogonus_fossarum_gilguy
#merge naucoris with N. opacus
invert.matrix.Bred$QH560199_Microvelia_sp. <- pmax(invert.matrix.Bred$QH560199_Microvelia_sp., invert.matrix.Bred$QH560117_Microvelia_douglasi)
invert.matrix.Bred$QH560117_Microvelia_douglasi <- NULL #delete Microvelia douglasi
#merge Enochrus sp. with E. deserticola
invert.matrix.Bred$QC111199_Enochrus_sp. <- pmax(invert.matrix.Bred$QC111199_Enochrus_sp., invert.matrix.Bred$QC111105_Enochrus_deserticola)
invert.matrix.Bred$QC111105_Enochrus_deserticola <- NULL #delete Enochrus deserticola
```

#create dissimilarity matrices
```{r}
invert.sim.P <- vegdist(invert.matrix.P, method="bray")
invert.sim.P
invert.sim.B <- vegdist(invert.matrix.B, method="bray")
invert.sim.B
```

#cluster analyses
```{r}
invert.clus.P <- agnes(invert.sim.P, metric = "bray", method = "average")
plot(invert.clus.P, title = NULL)
invert.clus.B <- agnes(invert.sim.B, metric = "bray", method = "average")
plot(invert.clus.B)
```


```{r}
invert.spec.P <-specaccum(t(invert.matrix.P), method="rarefaction")
invert.spec.P
```







